### 2017-11-16 aggregation/agg-foreground.tex
Supplementary stuffs

Figure~\ref{fig:fragments} illustrates the structure of some basic foreground configurations.  Most product system models would include many of these elements mixed together.  A reviewer with access to items \ref{itm:fg} and \ref{itm:af} in the disclosure would be able to construct $A_f$ and automatically create a process-flow diagram, annotated with information about each node.

@@

The first (a) is a sequential model, in which each node requires one foreground input and generates one output. This model is equivalent to a ``gate to gate'' model.  Here the weights $k_i$ indicate the amount of the preceding reference flow that is required by the subsequent node.  Figure~\ref{fig:fragments}(b) shows an additive model, in which the outputs of several foreground nodes are added together, equivalent to a ``mixer'' or a horizontal average.  In this arrangement the weights %represent the relative weights of each input, and
should add up to a unit output of the reference node.  Finally, Figure~\ref{fig:fragments}(c) shows a foreground model with a cyclic dependency, where some of the reference output is consumed by another foreground node.

@@

>>>>

@@

Figure~\ref{fig:fragments} illustrates the structure of some basic foreground configurations.  Most product system models would include many of these elements mixed together.  
The first (a) is a sequential model, in which each node requires one foreground input and generates one output. This model is equivalent to a ``gate to gate'' model.  Here the weights $k_i$ indicate the amount of the preceding reference flow that is required by the subsequent node.  Figure~\ref{fig:fragments}(b) shows an additive model, in which the outputs of several foreground nodes are added together, equivalent to a ``mixer'' or a horizontal average.  In this arrangement the weights %represent the relative weights of each input, and
should add up to a unit output of the reference node.  Finally, Figure~\ref{fig:fragments}(c) shows a foreground model with a cyclic dependency, where some of the reference output is consumed by another foreground node.

@@

As noted, a reviewer with access to items \ref{itm:fg} and \ref{itm:af} in the disclosure would be able to construct $A_f$ and automatically create a process-flow diagram, annotated with information about each node.

### 2017-11-16 aggregation/agg-requirements.tex
comparative review?
Late afternoon read through
Supplementary stuffs

>>>>

It may be observed that many LCA studies make use of data sources that have been previously published but that have not been included in any LCI reference or background database.  As long as these data sources can be integrated seamlessly into an LCA computation, it is not necessary to reproduce them in a disclosure.  However, in most applications, previously published data must be re-implemented by the author in the LCA software context, and often this re-implementation requires a re-interpretation of the data source as a unit process inventory, where one exchange is recognized as a reference flow and other exchange values are reported in proportionality to the reference flow.

Because of these conditions, in the vast majority of cases the LCA study disclosure must include the author's reimplementations in order to achieve both the aims for authority and primacy.  In so doing, the disclosure enables a critical reviewer to evaluate whether the author's implementations are generally correct and complete.

In the future, the inclusion of external data automatically can be accomplished in the same way that reference LCI data could conceivably be included automatically: by the data providers making their information available  using a stable semantic reference to a specialized Web-based application programming interface (API).  This would have the benefits of enabling downstream users to access the information without having to re-implement it, thus reducing the size of the disclosure necessary to describe the PSM and simplifying the task of the modeler.

### 2017-11-16 figures/aluminum-secondary.tex
Supplementary stuffs

{\scriptsize\sffamily
\begin{tabularx}{\textwidth}{|>{\hangindent=2ex}X|c@{~}c@{~}c@{~}c@{~}|c|}
\hline
\everypar{\hangindent1em \hangafter1}
(node) Foreground flow \rule[-3pt]{0pt}{12pt} & 0 & 1 & 2 & 3 & \\ 
\hline
(0) Aluminum, secondary, ingot, from automotive scrap, at plant (kg) [RNA] & \refbox  &  &  &  & \\ 
(1) Aluminum recovery, transport, to plant (kg) [RNA] & 1.03 & \refbox  &  &  & \\ 
(2) Quicklime, at plant (kg) [RNA] & 2.35e-05 &  & \refbox  &  & \\ 
(3) Limestone, at mine (kg) [RNA] &  &  & 1.87 & \refbox  & \\ 
\hline
Foreground Node Weights $\tilde{x}$ &    1 & 1.03 & 2.35e-05 & 4.39e-05& \\ 
\hline
Input: CUTOFF Disposal, solid waste, unspecified, to sanitary landfill [CUTOFF Flows] & \dependency &  & \dependency &  & 0.0842\\ 
Input: CUTOFF Filter media, at plant [CUTOFF Flows] & \dependency &  &  &  & 4.79e-05\\ 
Input: CUTOFF Lube oil, at plant [CUTOFF Flows] & \dependency &  &  &  & 8.75e-07\\ 
Input: CUTOFF Treatment gases, unspecified, at plant [CUTOFF Flows] & \dependency &  &  &  & 0.003\\ 
Input: CUTOFF Alloying additives, at plant [CUTOFF Flows] & \dependency &  &  &  & 0.021\\ 
Input: CUTOFF Chemicals, unspecified, used for wastewater treatment [CUTOFF Flows] & \dependency &  &  &  & 0.008\\ 
Input: CUTOFF Grain refiners, at plant [CUTOFF Flows] & \dependency &  &  &  & 0.0003\\ 
Input: CUTOFF Treatment salts, unspecified, at plant [CUTOFF Flows] & \dependency &  &  &  & 0.009\\ 
Input: CUTOFF Packaging, unspecified, at plant [CUTOFF Flows] & \dependency &  &  &  & 1.67e-05\\ 
Input: CUTOFF Aluminum scrap, automotive [CUTOFF Flows] & \dependency &  &  &  &  1.03\\ 
\hline
\hline
Background Dependencies \rule[-3pt]{0pt}{12pt} & 0 & 1 & 2 & 3 & $\tilde{a_d}$\\ 
\hline
Diesel, combusted in industrial boiler (l) [RNA] &  &  & \dependency & \dependency & 4.79e-08\\ 
Transport, train, diesel powered (t*km) [RNA] &  & \dependency & \dependency &  & 0.0415\\ 
Electricity, at grid, US, 2000 (kWh) [RNA] & \dependency &  & \dependency & \dependency & 0.668\\ 
Transport, combination truck, diesel powered (t*km) [RNA] &  & \dependency & \dependency &  & 0.374\\ 
Natural gas, combusted in industrial boiler (m3) [RNA] & \dependency &  & \dependency & \dependency & 0.223\\ 
Bituminous coal, combusted in industrial boiler (kg) [RNA] &  &  & \dependency & \dependency & 4.04e-06\\ 
Gasoline, combusted in equipment (l) [RNA] &  &  &  & \dependency & 2.25e-09\\ 
Liquefied petroleum gas, combusted in industrial boiler (l) [RNA] &  &  & \dependency &  & 7.57e-10\\ 
Transport, barge, average fuel mix (t*km) [RNA] &  &  & \dependency &  & 5.66e-07\\ 
\hline
Foreground Emissions \rule[-3pt]{0pt}{12pt} & 0 & 1 & 2 & 3 & $\tilde{b_f}$\\ 
\hline
Output: Lead [air, unspecified] & \dependency &  &  &  & 2.16e-07\\ 
Output: Suspended solids, unspecified [water, unspecified] & \dependency &  &  &  & 2.56e-05\\ 
Output: Particulates, unspecified [air, unspecified] & \dependency &  & \dependency & \dependency & 1.78e-07\\ 
Output: NMVOC, non-methane volatile organic compounds [air, unspecified] & \dependency &  &  &  & 4.7e-05\\ 
Output: BOD5, Biological Oxygen Demand [water, unspecified] & \dependency &  &  &  & 1.35e-09\\ 
Output: COD, Chemical Oxygen Demand [water, unspecified] & \dependency &  &  &  & 8.3e-07\\ 
Output: Sulfur dioxide  [air, unspecified] &  &  & \dependency &  & 3.52e-09\\ 
Output: Dissolved solids [water, unspecified] & \dependency &  &  &  & 2.38e-08\\ 
Output: carbon dioxide [air, unspecified] &  &  & \dependency &  & 1.8e-05\\ 
Input: Limestone [resource, ground-] &  &  &  & \dependency & 4.39e-05\\ 
Output: Heavy metals, unspecified [water, unspecified] & \dependency &  &  &  & 2.25e-05\\ 
Output: Organic substances, unspecified [water, unspecified] & \dependency &  &  &  & 1.29e-06\\ 
Output: Acids, unspecified [air, unspecified] & \dependency &  &  &  & 4.31e-05\\ 
\hline
\end{tabularx}
}

>>>>

{\scriptsize\sffamily
\begin{tabularx}{\textwidth}{|>{\hangindent=3ex}X|c@{~}c@{~}c@{~}c@{~}|c|}
\hline
(node) Foreground flows -- $A_f$ \rule[-3pt]{0pt}{12pt} & 0 & 1 & 2 & 3 & \\ 
\hline
(0) Aluminum, secondary, ingot, from automotive scrap, at plant [RNA] (kg) & \refbox  &  &  &  & \\ 
(1) Aluminum recovery, transport, to plant [RNA] (kg) & 1.03 & \refbox  &  &  & \\ 
(2) Quicklime, at plant [RNA] (kg) & 2.35e-05 &  & \refbox  &  & \\ 
(3) Limestone, at mine [RNA] (kg) &  &  & 1.87 & \refbox  & \\ 
\hline
Foreground Node Weights $\tilde{x}$ &    1 & 1.03 & 2.35e-05 & 4.39e-05& \\ 
\hline
Input: CUTOFF Disposal, solid waste, unspecified, to sanitary landfill [CUTOFF Flows] (kg) & \dependency &  & \dependency &  & 0.0842\\ 
Input: CUTOFF Filter media, at plant [CUTOFF Flows] (kg) & \dependency &  &  &  & 4.79e-05\\ 
Input: CUTOFF Lube oil, at plant [CUTOFF Flows] (kg) & \dependency &  &  &  & 8.75e-07\\ 
Input: CUTOFF Treatment gases, unspecified, at plant [CUTOFF Flows] (kg) & \dependency &  &  &  & 0.003\\ 
Input: CUTOFF Alloying additives, at plant [CUTOFF Flows] (kg) & \dependency &  &  &  & 0.021\\ 
Input: CUTOFF Chemicals, unspecified, used for wastewater treatment [CUTOFF Flows] (kg) & \dependency &  &  &  & 0.008\\ 
Input: CUTOFF Grain refiners, at plant [CUTOFF Flows] (kg) & \dependency &  &  &  & 0.0003\\ 
Input: CUTOFF Treatment salts, unspecified, at plant [CUTOFF Flows] (kg) & \dependency &  &  &  & 0.009\\ 
Input: CUTOFF Packaging, unspecified, at plant [CUTOFF Flows] (kg) & \dependency &  &  &  & 1.67e-05\\ 
Input: CUTOFF Aluminum scrap, automotive [CUTOFF Flows] (kg) & \dependency &  &  &  &  1.03\\ 
\hline
\hline
Background Dependencies -- $A_d$ \rule[-3pt]{0pt}{12pt} & 0 & 1 & 2 & 3 & $\tilde{a_d}$\\ 
\hline
Transport, barge, average fuel mix [RNA] (t*km) &  &  & \dependency &  & 5.66e-07\\ 
Liquefied petroleum gas, combusted in industrial boiler [RNA] (l) &  &  & \dependency &  & 7.57e-10\\ 
Transport, combination truck, diesel powered [RNA] (t*km) &  & \dependency & \dependency &  & 0.374\\ 
Diesel, combusted in industrial boiler [RNA] (l) &  &  & \dependency & \dependency & 4.79e-08\\ 
Natural gas, combusted in industrial boiler [RNA] (m3) & \dependency &  & \dependency & \dependency & 0.223\\ 
Transport, train, diesel powered [RNA] (t*km) &  & \dependency & \dependency &  & 0.0415\\ 
Electricity, at grid, US, 2000 [RNA] (kWh) & \dependency &  & \dependency & \dependency & 0.668\\ 
Bituminous coal, combusted in industrial boiler [RNA] (kg) &  &  & \dependency & \dependency & 4.04e-06\\ 
Gasoline, combusted in equipment [RNA] (l) &  &  &  & \dependency & 2.25e-09\\ 
\hline
Foreground Emissions -- $B_f$ \rule[-3pt]{0pt}{12pt} & 0 & 1 & 2 & 3 & $\tilde{b_f}$\\ 
\hline
Output: Lead [air, unspecified] (kg) & \dependency &  &  &  & 2.16e-07\\ 
Output: Suspended solids, unspecified [water, unspecified] (kg) & \dependency &  &  &  & 2.56e-05\\ 
Output: Particulates, unspecified [air, unspecified] (kg) & \dependency &  & \dependency & \dependency & 1.78e-07\\ 
Output: NMVOC, non-methane volatile organic compounds [air, unspecified] (kg) & \dependency &  &  &  & 4.7e-05\\ 
Output: BOD5, Biological Oxygen Demand [water, unspecified] (kg) & \dependency &  &  &  & 1.35e-09\\ 
Output: COD, Chemical Oxygen Demand [water, unspecified] (kg) & \dependency &  &  &  & 8.3e-07\\ 
Output: Sulfur dioxide  [air, unspecified] (kg) &  &  & \dependency &  & 3.52e-09\\ 
Output: Dissolved solids [water, unspecified] (kg) & \dependency &  &  &  & 2.38e-08\\ 
Output: carbon dioxide [air, unspecified] (kg) &  &  & \dependency &  & 1.8e-05\\ 
Input: Limestone [resource, ground-] (kg) &  &  &  & \dependency & 4.39e-05\\ 
Output: Heavy metals, unspecified [water, unspecified] (kg) & \dependency &  &  &  & 2.25e-05\\ 
Output: Organic substances, unspecified [water, unspecified] (kg) & \dependency &  &  &  & 1.29e-06\\ 
Output: Acids, unspecified [air, unspecified] (kg) & \dependency &  &  &  & 4.31e-05\\ 
\hline
\end{tabularx}
}
